The vertical Fermi and eROSITA bubbles inclined jets: A proof-of-concept study

### 2021-12-26 paper.tex
update

  \subsection{The Galactic and Disk Models}
  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
  by an external plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  The pyFC randomly generates dimensionless 3D scalar field $f_{\text{clumpy}}(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu_{\text{clumpy}}$ and dispersion $\sigma_{\text{clumpy}}$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f_{\text{clumpy}}(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\

  Finally, we multiply $f_{\text{clumpy}}(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
  to obtain the density of ISM disk $\rho_{\text{ismDisk}}(\bold{x})$. i.e.\
  $\displaystyle\rho_{\text{ismDisk}}(\bold{x}) =\
  f_{\text{clumpy}}(\bold{x}) \rho_{\text{isoDisk}}(z)$.

  The temperature in each cell of the disk is determined by pressure equilibrium with hot gas.\

  The porosity of the warm phase arises by imposing an upper temperature cutoff for the\
  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
  are deemed thermally unstable.

@@

%  \begin{enumerate}
%     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(z)$ by \Cref{isothermal-disk-density}.
%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f_{\text{clumpy}}$ obeying\
%           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
%     \item \Cref{density-ism-disk}.
%     \item
%  \end{enumerate}

\begin{table*}[t]
\raggedright
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disk }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disk                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disk }                    &                                           &                                      &                                \\
$T_{\text{\text{c}}}$                 & Critical temperature of warm atomic phase & $10^{4}$ K                           & \citep{peak-ism-density}       \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                &   N/A                          \\
$\mu_{\text{clumpy}}$                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma_{\text{clumpy}}$     & Dispersion of scalar field                & 2.2                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
      \item    $\ddag$  $\sigma_{\text{clumpy}}=$ ....
    \end{tablenotes}
\end{table*}

>>>>

  \subsection{The Galactic and Disk Models}
  As a proof-of-concept study, we approximate conventionally axisymmetric stellar potential of Milky Way\
  by an plane-parallel potential that is symmetric about the mid-plane $z=0$\
  in a simulation box size of\
  $14\times14\times28$ kpc, slightly larger than the size of eROISTA bubbles.

@@

  pyFC randomly generates dimensionless 3D scalar field $f(\bold{x})$\ % that is clumpy and porous.
  that obeys the log-normal probability distribution\
  with mean $\mu$ and dispersion $\sigma$,\
  and follows the power-law Kolmogorov spectrum
  \begin{equation}
    D(\bold{k})=\int k^{2} \hat{f}(\bold{k})\hat{f}^{*}(\bold{k})d\Omega \propto k^{-\beta},
    \label{Kolmogorov-spectrum}
  \end{equation}
  where $\hat{f}(\bold{k})$ is the Fourier transform of $f(\bold{x})$.\
  The spectrum $D(\bold{k})$ in the Fourier space is characterized by the power law index $\beta=5/3$,\
  the Nyquist limit $k_{\text{max}}$, and the lower cutoff wave number $k_{\text{min}}$.
  $k_{\text{max}}$ is one-half of the spatial resolution within disk,\
  and $k_{\text{min}}$ is 375.0, corresponding to the maximum size of an individual clump $\sim 20$ pc.\

  \begin{enumerate}
     \item  We multiply $f(\bold{x})$ and $\rho_{\text{isoDisk}}(z)$\
            to obtain the density of disk $\tilde{\rho}_{\text{ismDisk}}(\bold{x})$. i.e.\
            $\displaystyle\tilde{\rho}_{\text{ismDisk}}(\bold{x}) =\
            f(\bold{x}) \rho_{\text{isoDisk}}(z)$.\
            The temperature is determined by
            $\displaystyle \tilde{T}_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\tilde{\rho}_{\text{ismDisk}}$.
     \item  If $\tilde{T}_{\text{ismDisk}}$ larger than $T_{\text{crit}}$,
  \end{enumerate}

  The porosity of the disk arises by imposing an upper temperature cutoff for the\
  existence of clouds at $T_{\text{crit}} = 10^{4}$ K, beyond which clouds
  are deemed thermally unstable and replaced by temperature of atmosphere.

  The temperature in each cell within the disk is determined by pressure equilibrium with hot gas.\
  The clouds within the disk are in pressure equilibrium with the surrounding hot voids, thus\
  $\displaystyle T_{\text{ismDisk}} = T_{\text{isoDisk}}\rho_{\text{isoDisk}}/\rho_{\text{ismDisk}}$.

@@

%  \begin{enumerate}
%     \item Constructing the isothermal disk $\rho_{\text{isoDisk}}(z)$ by \Cref{isothermal-disk-density}.
%     \item Using PyFC code to obtain a dimensionless clumpy distribution $f$ obeying\
%           lognormal distribution and the power-law spectrum, \Cref{Kolmogorov-spectrum}.
%     \item \Cref{density-ism-disk}.
%     \item
%  \end{enumerate}

\begin{table*}[t]
\raggedright
\caption{Parameters of the disk, atmosphere, and gravitational potential in the simulation.}
\label{table-parameters}
\begin{tabular}{@{}llrc@{}}
\toprule[1pt]\midrule[0.3pt]
Parameter                             & Description                               & Value                                &  Reference                     \\ \midrule
{\bf Static stellar potential }       &                                           &                                      &                                \\
$\sigma_{\text{bulge}}$               & Velocity dispersion of bulge              & 100 km$\cdot$s$^{-1}$                & \citep{velocity-dispersion-MW} \\
$\rho_{\text{bulge}}^{\text{peak}}$   & Peak average density of bulge             & $4\times 10^{-24}$ g$\cdot$cm$^{-3}$ &   N/A                          \\ \hline
{\bf Static dark halo potential }     &                                           &                                      &                                \\
$v_{\text{halo}}$                     &                                           & 131.5 km$\cdot$s$^{-1}$              & \citep{Johnston1995}           \\
$d_{\text{h}}$                        & Core radius                               & 12 kpc                               & \multicolumn{1}{c}{''}         \\ \hline
{\bf Atmosphere }                     &                                           &                                      &                                \\
$T_{\text{\text{atmp}}}$              & Temperature of atmosphere                 & $10^{6}$ K                           & \citep{temperature-MW}         \\ \hline
{\bf Isothermal disk }                &                                           &                                      &                                \\
$z_{0}$                               & Scale height of disk                      & 100 pc                               & \citep{peak-ism-density}       \\
$T_{\text{\text{isoDisk}}}$           & Temperature of disk                       & $10^{3}$ K                           & \multicolumn{1}{c}{''}         \\
$\rho_{\text{isoDisk}}^{\text{peak}}$ & Peak mass density of disk                 & $10^{-23}$ g$\cdot$cm$^{-3}$         & \multicolumn{1}{c}{''}         \\ \hline
{\bf Clumpy disk }                    &                                           &                                      &                                \\
$T_{\text{\text{c}}}$                 & Critical temperature of warm atomic phase & $10^{4}$ K                           & \citep{peak-ism-density}       \\
$\dagger$  $k_{\text{min}}$           & Cutoff wave number                        & 375.0                                &   N/A                          \\
$\mu$                                 & Mean of scalar field                      & 1.0                                  &   N/A                          \\
$\ddag$  $\sigma$                     & Dispersion of scalar field                & 2.2                                  & \citep{Federrath2010}          \\
$\beta$                               & Power law index                           & -5/3                                 &   N/A                          \\ \midrule
\end{tabular}
\begin{tablenotes}
      \raggedright
      \item  $\dagger$  $k_{\text{min}}=375.0$ leads to the size of an individual clump $\sim 100$ pc.
      \item    $\ddag$  $\sigma=$ ....
    \end{tablenotes}
\end{table*}
